\documentclass[runningheads]{llncs}
\usepackage[spanish]{babel}
\usepackage{graphicx}

\begin{document}
%
\title{Network-attached storage system}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jairo Sánchez Rodríguez\inst{1}\orcidID{0000-0002-5811-9106} \and
Luis Guillermo Castilla\inst{1}\and
Juan Sebastían Arguello\inst{1}\and
Luis Antonio Diaz\inst{1}\and
Silvia Juliana Pabón\inst{1}\and
Daniel Alberto Salazar\inst{1}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universidad Pontificia Bolivariana,\\ Campus Universitario Km 7 vía Piedecuesta, Colombia,
\email{info@upb.edu.co}\\
\url{https://www.upb.edu.co/es/home}
}
%
\maketitle              
%
\input{content/introduccion/abstract.tex}
%
\section{Introducción}
\input{content/introduccion/introduccion.tex}
%
\section{Marco Teórico}
\input{content/marcoConceptual/marco_conceptual.tex}
%
\section{Objetivos}
\input{content/objetivos/objetivos.tex}
%
\section{Metodología}
\input{content/metodologia/metodologia.tex}
%
\section{Avances}
\input{content/avances/avances.tex}
%
\section{Cronograma}
\input{content/cronograma/cronograma.tex}
%
\section{Conclusiones}
\input{content/conclusiones/conclusiones.tex}
%
\section{Trabajo futuro}
\input{content/futuro/futuro.tex}
%
\section{Agradecimientos}
\input{content/agradecimientos/agradecimientos.tex}
%
\section{Anexos}
\input{anexos/anexos.tex}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}
